Supplemental Material for\\Evaluating `Graphical Perception' with CNNs

### 2018-03-31 PAPER/SUPPLEMENTAL/supplemental.tex
Updates.

%% the only exception to this rule is the \firstsection command
\begin{figure*}
\centering
This material contains several plots accompanying the main manuscript.
\end{figure*}
\clearpage
\begin{figure*}[t]
	\centering
	  \includegraphics[width=.8\linewidth]{error_inspection_new.pdf}
  \caption{\textbf{Error Distributions.} Error distributions of our networks when decoding elementary perceptual tasks.}
	\label{fig:errors}
\end{figure*}

\begin{figure*}[t]
	\centering
	  \includegraphics[width=\linewidth]{cross_network_new.pdf}
  \caption{\textbf{Cross-Network Validation.} Our networks fail when the stimuli is translated.}
	\label{fig:cross_network}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.48\linewidth]{../gfx/figure1_slim_left.pdf}
	  \includegraphics[width=.48\linewidth]{../gfx/figure1_slim_right.pdf}
  \caption{\textbf{Cross-Network Validation.} Our networks fail when the stimuli is translated.}
	\label{fig:cross_network}
\end{figure*}

\begin{figure}[t]
	\centering
	  \includegraphics[width=\linewidth]{../gfx/figure3_mlae_better_all_AA.pdf}
  \caption{\textbf{Anti-Aliasing.} We test whether anti-aliasing effects the performance of our networks on pie charts by measuring MLAE. The difference is not statistically significant ($F(1,30)=0.341,p>0.5$).}
	\label{fig:aa}
\end{figure}

>>>>

%% the only exception to this rule is the \firstsection command
\begin{figure*}
\centering
This material contains several plots accompanying the main manuscript.
\end{figure*}
\clearpage
\begin{figure*}[t]
	\centering
	  \includegraphics[width=.8\linewidth]{error_inspection_new.pdf}
  \caption{\textbf{Error distributions.} Error distributions of our networks when decoding elementary perceptual tasks.}
	\label{fig:errors}
\end{figure*}

\begin{figure*}[t]
	\centering
	  \includegraphics[width=\linewidth]{cross_network_new.pdf}
  \caption{\textbf{Cross-network variability.} Our networks fail when the stimuli changes through translation or stroke width. The x-labels indicate the training configuration while the y-labels indicate the stimuli variation. Numbers represent MLAE.}
	\label{fig:cross_network}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=.48\linewidth]{../gfx/figure1_slim_left.pdf}
	  \includegraphics[width=.48\linewidth]{../gfx/figure1_slim_right.pdf}
  \caption{\textbf{Elementary perceptual tasks.} Midmean logistic absolute errors (MLAE) for all generated stimuli and across all networks. The * indicates networks which use ImageNet weights instead of bein trained from scratch.}
	\label{fig:cross_network}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=\linewidth]{../gfx/figure1_boxplot_new.pdf}
  \caption{\textbf{Elementary perceptual tasks.} Midmean logistic absolute errors (MLAE) visualized as box plots.}
	\label{fig:cross_network}
\end{figure*}

\begin{figure}[t]
	\centering
	  \includegraphics[width=\linewidth]{../gfx/figure3_mlae_better_all_AA.pdf}
  \caption{\textbf{Anti-aliasing.} We test whether anti-aliasing effects the performance of our networks on pie charts by measuring MLAE. The difference is not statistically significant ($F(1,30)=0.341,p>0.5$).}
	\label{fig:aa}
\end{figure}
